\documentclass[a4paper,12pt]{article}

\usepackage[a4paper,
            left=1in,
            right=1in,
            top=0.5in,
            bottom=0.5in
           ]{geometry}
           
\usepackage{tabularx}
\renewcommand{\arraystretch}{1.2}           

%% 1) Load fontspec first
\usepackage{fontspec}
\setmainfont[
  Path           = /usr/local/texlive/2025/texmf-dist/fonts/opentype/adobe/sourcecodepro/,
  Extension      = .otf,
  UprightFont    = *-Regular,
  ItalicFont     = *-RegularIt,
  BoldFont       = *-Bold,
  BoldItalicFont = *-BoldIt,
  Scale          = MatchLowercase,
  %Scale          = 0.9,
]{SourceCodePro}

\usepackage[breaklinks=true,colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}



\begin{document}
\thispagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{center}
\begin{tabular}{ccc}
&\Large \textbf{Résumé}&\\
\\
& Ramūnas Girdziušas &\\  
& Laisvės pr. 67-54, Vilnius, LT-07189 &\\
& aabbtree77[at]gmail.com &\\
& \url{https://aabbtree77.github.io/} &\\
\end{tabular}
\end{center}
%
\section*{Education}
%
\begin{tabularx}{\textwidth}{@{}p{3cm}X@{}}
1995 - 1999  & B.Sc. (E. Eng.), Vilnius Gediminas Technical University\\
1999 - 2008  &  M.Sc., D.Sc. (Tech.), Helsinki University of Technology\\
\end{tabularx}
%
\section*{Employment}
%
\begin{tabularx}{\textwidth}{@{}p{3cm}X@{}}
2014 - Now & Self-Funded \\

2013 - 2014 &
Faculty of Informatics at the University of Lugano\\

2011 - 2012 &
École Nationale Supérieure des Mines de Saint-Étienne\\

2008 - 2009 &
Dep. of Neurobiology at the University of California, LA \\

2000 - 2008 &
Dep. of Comp. Sc. at Helsinki University of Technology\\
\end{tabularx}

\section*{Selected Projects}
\label{sect:pubs}

\begin{tabularx}{\textwidth}{@{}p{3cm}X@{}}

\href{https://github.com/aabbtree77/miniguestlog}{miniguestlog} & Built and maintained location tracking web app.\\
               2025    & MERN, render.com, mongodb.com, MaxMind GeoLite2, BearVPN\\
                       &\\
\href{https://github.com/aabbtree77/law2}{lawtrust.eu} & Made a lawyer more visible on MS Bing.\\
               2024    & RWD, i18n, porkbun.com, github pages, SEO, HTTPS, Go\\
                       &\\
\href{https://github.com/aabbtree77/esp32-vpn}{esp32-vpn} & Connected ESP32 devices globally without 3rd party.\\
               2023    & IoT, VPN, P2P, MQTT, SSH, Wi-Fi, 24/7, MicroPython, Go\\
                       &\\
\href{https://github.com/aabbtree77/twinpeekz2}{twinpeekz2}    & Implemented real-time multi-pass 3D rendering pipeline.\\
                   2022       & GLFW, GLTF, OpenGL, RenderDoc, ray marching, Nim, Go\\
                          &\\
\href{https://github.com/aabbtree77/adast}{adast} & Wrote and maintained firmware for a factory machine. \\
2020 - 2024 & Adast Maxima MS80, paper guillotine, avr-gcc, ATmega16 \\
     &\\                        
\href{https://hal.archives-ouvertes.fr/hal-00723427}{hal-00723427} & Sped up Monte Carlo integration in a complex eng. project.\\
                     2012 & Fluid dynamics, Bayesian opt., ProActive PACA Grid\\
                          &  \\        
\end{tabularx}

%
\section*{Awards}
%
\begin{tabularx}{\textwidth}{@{}p{3cm}X@{}}
        2008 & Doctoral thesis award: “Pass with Distinction”\\
        1999 - 2000 & Nokia scholarship
\end{tabularx}

\end{document}
